--- 
title: "WILD 6900 Final Project"
author: "Sarah Kapel"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
# url: your book url like https://bookdown.org/yihui/bookdown
description: |
  This bookdown contains my final project for Reproducible Science 2023. For 
  this project, I used my own data from my research. The first chapter will 
  provide some context to my research and also explain how I reorganized my 
  original datasheets after learning about good spreadsheet practices. In the 
  second chapter,I demonstrate how I created a database for each aspen seedling. 
  In the third chapter, I visualize simulated data to see how to illustrate 
  my future results. 
  
link-citations: yes
github-repo: rstudio/bookdown-demo
---

# My Final Project

  This bookdown contains my final project for Reproducible Science 2023. For 
  this project, I used my own data from my research. The first chapter will 
  provide some context to my research and also explain how I reorganized my 
  original datasheets after learning about good spreadsheet practices. In the 
  second chapter,I demonstrate how I created a database for each aspen seedling. 
  In the third chapter, I visualize simulated data to see how to illustrate 
  my future results. 

```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
